Comment on Hodgkins et al. (2018)

### 2023-12-06 analysis/paper/002-reply-main.Rmd
Prepare submission of the reply to EarthEarXiv.
Update link to reproducible research compendium in manuscript 2.

---
title: 'Comment on Hodgkins et al. (2018)'
author: "Henning Teickner$^{1, *}$, Klaus-Holger Knorr$^1$"
date: ""
output: 
  bookdown::pdf_book:
    keep_tex: true
    toc: false
bibliography: references.bib
header-includes:
   - \usepackage{float}
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{titling}
   - \pretitle{\begin{center}
     \bf{This manuscript is a non-peer reviewed preprint submitted to EarthArXiv. It has not been submitted for publication to a journal yet.} \LARGE\\
     \vspace{5ex}}
   - \posttitle{\end{center}}
fontsize: 12pt
abstract:  |  
   \noindent @Hodgkins.2018 used mid infrared spectra (MIRS) to make inferences about the stability of peat against decomposition along a latitudinal gradient from the tropics to northern latitudes. Recently, we have shown that these spectral prediction models are biased and their predictions more uncertain than considered in @Hodgkins.2018 [@Teickner.2022f]. Here, we show what consequences this bias and uncertainty and additional neglected uncertainty sources have for the main conclusions in @Hodgkins.2018.  
   In particular, we find that:

      3. More research should focus on how estimates of carbohydrate and aromatic contents from MIRS may be confounded by other organic matter fractions, in particular proteins. As a first step, this requires accurate concepts to name organic matter fractions and variables used in the interpretation of MIRS.
---

@@

Data and code to reproduce our analyses are available via <https://doi.org/10.5281/zenodo.6325760>.

>>>>

---
title: 'Comment on Hodgkins et al. (2018)'
author: "Henning Teickner$^{1, *}$, Klaus-Holger Knorr$^1$"
date: ""
output: 
  bookdown::pdf_book:
    keep_tex: true
    toc: false
bibliography: references.bib
header-includes:
   - \usepackage{float}
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{titling}
   - \pretitle{\begin{center}
     \bf{This manuscript is a non-peer reviewed preprint submitted to EarthArXiv. It has not been submitted for publication to a journal yet.} \LARGE\\
     \vspace{5ex}}
   - \posttitle{\end{center}}
fontsize: 12pt
---

@@

Data and code to reproduce our analyses are available via <https://doi.org/10.5281/zenodo.10276230> [@Teickner.2023a].
